Discrete Quantum Theories and Computing

### 2019-01-29 dissertation.tex
dissertation.lyx Acknowledgments Updating according to Amr's suggestion...

 &  & Supervisor &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop

@@

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
is organized in the term paper for SLST-T501 Academic Writing course.
I want to thank Prof.\ Tom Lewis for proof-reading them, and they
become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
you even if your name is not listed here, and sorry for my bad memory.\todo{Acknowledgments
cleaned up until here. }

Many people in both departments of Mathematics and Computer Science
need to do something more to make my double-major works smoothly.
I need to thank all of them, especially directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge and Prof.\ Matthias
Weber; directors of Ph.D. study in Computer Science, especially Prof.\ Yuqing
Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.

@@

\item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
what I did in the perspective of a general PhD. in Physics and working
later in more computational industry.

@@

Finally, thank Jin-Ru Yang (楊謹如) for everything could not be written
here.\end{acknowledgments*}

>>>>

 &  & Supervisor &  &  &  &  & The application for ``Rethinking Foundations of Physics'' 2017 workshop

@@

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
is organized in the term paper for SLST-T501 Academic Writing course.
I want to thank Prof.\ Tom Lewis for proof-reading them, and they
become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
you even if your name is not listed here, and sorry for my bad memory.

Many people in both the departments of Mathematics and Computer Science
have done everything to make my double-major smooth. \todo{Acknowledgments
cleaned up until here. }I need to thank all of them, especially directors
of graduate study in Mathematics, especially Prof.\ Christopher Judge
and Prof.\ Matthias Weber; directors of Ph.D. study in Computer Science,
especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}.

@@

\item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
what I did from the perspective of a general PhD. in Physics and working
later in more computational industry.

@@

Finally, I thank Jin-Ru Yang (楊謹如) for everything that could not be
written here.\end{acknowledgments*}
